%% Title
\titlepage[of Peterhouse]{%
  A dissertation submitted to the University of Cambridge\\ for the degree of Doctor of Philosophy}

%% Abstract
\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
  %\thispagestyle{empty}
The Standard Model has been a successful theory in describing the behaviour of fundamental particles, but there are still problems remaining unsolved. New theoretical models are therefore proposed to answer those questions with either new interactions or new particles. This thesis is presenting the searches for new physics signatures in the two forms from LHC $\sqrt{s}=13~TeV$ collisions with the ATLAS detector. The data was collected in 2015 and 2016 corresponding to the integrated luminosity of $36.1~fb^{-1}$
\\
\\And, both the LHC and ATLAS detector are now going through the upgrades for the operation in 2021 with the $\sqrt{s}=14TeV$ collisions. This thesis will also show the ongoing upgrade work for the hardware calorimeter trigger.    
\end{abstract}


%% Declaration
\begin{declaration}
  This dissertation is the result of my own work, except where explicit
  reference is made to the work of others, and has not been submitted
  for another qualification to this or any other university. This
  dissertation does not exceed the word limit for the respective Degree
  Committee.
  \vspace*{1cm}
  \begin{flushright}
    Andy Buckley
  \end{flushright}
\end{declaration}


%% Acknowledgements
\begin{acknowledgements}
  Of the many people who deserve thanks, some are particularly prominent,
  such as my supervisor\dots
\end{acknowledgements}


%% Preface
\begin{preface}
  This thesis describes my research on various aspects of the \LHCb
  particle physics program, centred around the \LHCb detector and \LHC
  accelerator at \CERN in Geneva.

  \noindent
  For this example, I'll just mention \ChapterRef{chap:SomeStuff}
  and \ChapterRef{chap:MoreStuff}.
\end{preface}

%% ToC
\tableofcontents


%% Strictly optional!
\frontquote{%
  We are just an advanced breed of monkeys on a minor planet of a very average star. But we can understand the Universe. That makes us something very special.}%
  {Stephen Hawking}
%% I don't want a page number on the following blank page either.
\thispagestyle{empty}
